Generate Networks

### 2015-08-23 code/01_generate_networks.Rmd
find matching size R

opts_knit$set (root.dir=normalizePath('../'))
opts_chunk$set (fig.path = "./figures/01/")
opts_chunk$set (cache.path = "./cache/02/")
opts_chunk$set (fig.width = 11, 
                fig.height = 9,
                out.width = "858px")
```

@@

```{r}
plyr::ldply(m_match, function(x){
	data.frame(matching_size = x$match$matching_size,
						 n_pla = table(igraph::V(x$net)$type)["pla"],
						 n_pol = table(igraph::V(x$net)$type)["pol"],
						 n_int = length(igraph::E(x$net)$weight),
						 matching_weight = x$match$matching_weight,
						 sum_weight = sum(igraph::E(x$net)$weight))
}) %>% kable
```

>>>>

opts_knit$set (root.dir=normalizePath('../'))
opts_chunk$set (fig.path = "./figures/01/")
opts_chunk$set (cache.path = "./cache/01/")
opts_chunk$set (fig.width = 11, 
                fig.height = 9,
                out.width = "858px")
```

@@

```{r}
plyr::ldply(m_match, function(x){
	data.frame(matching_size = x$match$matching_size,
						 n_pla = table(igraph::V(x$net)$type)["pla"],
						 n_pol = table(igraph::V(x$net)$type)["pol"],
						 n_int = length(igraph::E(x$net)$weight),
						 matching_weight = x$match$matching_weight,
						 sum_weight = sum(igraph::E(x$net)$weight))
}) %>% 
	dplyr::mutate(n_comb = choose(n_int, matching_size)) %>%
	kable
```

The matching size and number of interactions doesn't coincide with the ones previously used for the bipartite matching.
